Analyzing Homelessness and Shelter Use in Toronto: A Data-Driven Approach

### 2024-09-26 paper/paper.qmd
changing axis label

ggplot(yearly_bed_capacity, aes(x = factor(year), y = Total_Bed_Capacity, fill = program_model)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Year", y = "Actual Bed Capacity") +
  theme_minimal()

@@

ggplot(monthly_data, aes(x = month, y = service_user_count, color = factor(year), group = year)) +
  geom_line(size = 1) +
  labs(x = "Month", y = "Service User Count", color = "Year") +
  theme_minimal() +
  scale_x_discrete(limits = month.abb)
```

>>>>

ggplot(yearly_bed_capacity, aes(x = factor(year), y = Total_Bed_Capacity, fill = program_model)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Year", y = "Actual Bed Capacity") +
  scale_y_continuous(labels = scales::comma) +
  theme_minimal()

@@

ggplot(monthly_data, aes(x = month, y = service_user_count, color = factor(year), group = year)) +
  geom_line(size = 1) +
  labs(x = "Month", y = "Service User Count", color = "Year") +
  theme_minimal() +
  scale_x_discrete(limits = month.abb) +
  scale_y_continuous(labels = scales::comma)
